---
title: "Cosim of C++ and Eplus"
---

This document show how to specify the path of .exe(C++ application) and conduct co-simulation with EnergyPlus .

## Here is the C++ code

```cpp
/*
 This C++ script is the example of CosimR to show how to do co-simulation with EnergyPlus
 The Code is messy because I'm not familiar with the C/C++. 
 You can open a issue and point how to modify it or make it clean.
 Package: CosimR
 Github:	https://github.com/jywang2016/CosimR
 Author: Jiangyu Wang
 Date: 11th Dec, 2018
 Email: jywang_2016@hust.edu.cn
 Reference: schedule example in BCVTB
 Compile: g++ -o Cosim Cosim.cpp -std=c++11
 */
#include <iostream>
#include <string>
#include <regex>
#include <stdio.h>
#include <stdlib.h>

using namespace std;

int main(int argc, char *argv[]){
  
  string error = "the Number of arguments are not correct!";
  if(argc !=4){
    cout<<error<<endl;
    return(1);
  }
  
  smatch result;
  string tempstr = argv[1];
  
  string regex_str("\\d+\\.?\\d*"); 
  regex pat(regex_str,regex::icase);
  
  string::const_iterator iter = tempstr.begin();
  string::const_iterator iterEnd= tempstr.end();
  string strouttemp;
  
  if(regex_search(iter,iterEnd,result,pat)){
    strouttemp = result[0]; //just need the first temperature info
    //cout<<outdoortemp<<endl;
  }
  
  int time;
  char *strtime = (char *) argv[2];
  time = atoi(strtime);
  
  float outtemp;
  char *strtemp = (char *) strouttemp.c_str();
  outtemp = atof(strtemp);
  
  // input const 
  const int DAYSTART = 6*3600;
  const int NIGHTSTART = 16*3600;
  const double TCNIGHT = 30.0;
  const double TCROOLOW = 22.0;
  const double TCROOHIG = 26.0;
  
  const double TCOUTLOW = 20.0;
  const double TCOUTHIG = 24.0;
  
  const double THDAY = 20.0;
  const double THNIGHT = 16.0;
  
  // temp set logic 
  
  double ToutDif;
  ToutDif = outtemp - TCOUTLOW;
  
  double TSetCooOn;
  TSetCooOn = TCROOLOW + ToutDif * (TCROOHIG - TCROOLOW)/(TCOUTHIG - TCOUTLOW);
  
  double TCDay;
  TCDay = max(TCROOLOW,min(TCROOHIG,TSetCooOn));
  
  double THSetPoi;
  double TCSetPoi;
  
  int timeOfDay = time % 86400;
  
  if(timeOfDay > DAYSTART && timeOfDay < NIGHTSTART){
    THSetPoi = THDAY;
    TCSetPoi = TCDay;
  }else{
    THSetPoi = THNIGHT;
    TCSetPoi = TCNIGHT;
  }
  
  cout<<THSetPoi<<","<<TCSetPoi<<", "<<endl;
  
  return 0;
}

```
Suppose the `Cosim.cpp` will be placed into the `cpp` folder under the `xmlpath = 'D:/bcvtb/examples/CosimRtest'`.
If you are a R user with Rtools installed or Linux user, you can use `g++ -o Cosim Cosim.cpp -std=c++11` to compile your codes. Then, place the `Cosim.exe` file into the `./cpp` folder.

## Co-simulation by using CosimR

```{r}
library(CosimR)
```

Step1: generate the .xml file

```{r,eval=TRUE}
xmlpath = 'D:/bcvtb/examples/CosimRtest'
copy_xml(xmlpath = xmlpath)
```

Step2: modify the .xml file

```{r}
file.copy(from = system.file("extdata/Cosim.exe", package = "CosimR"),
          to = paste0(xmlpath,'/cpp'),
          overwrite = TRUE)

xmlroot<- modify_xml(xmlpath = xmlpath,
                     timeStep = 15*60, 
                     beginTime = 3*24*3600,
                     endTime = 4*24*3600,
                     extractLength = 2,
                     idf = paste0(xmlpath,'/SmOffPSZ.idf'),
                     epw = 'D:/bcvtb/examples/ePlusWeather/USA_IL_Chicago-OHare.Intl.AP.725300_TMY3.epw',
                     outname = 'eplusout',
                     programname = 'D:/bcvtb/examples/CosimRtest/cpp/Cosim',
                     programArgs = '',
                     workingDir = paste0(xmlpath,'/cpp'),
                     cpp = TRUE)
```

Step3: save the .xml file

```{r}
write_xml(rootnode = xmlroot,
          xmlpath = xmlpath,
          output = 'new.xml')
```

Step4: run the .xml file

```{r,eval=FALSE}
run_Cosim(bcvtbpath = 'D:/bcvtb',
          xmlpath = xmlpath,
          output = 'new.xml')
```

## Add plotter in BCVTB manually

Plotter block is not included in the .xml template file provided in the `CosimR` package. If you want see the results in real time, add plotter block in BCVTB manually is a good choice.