---
title: "Cosim of Python and Eplus"
---

This document show how to specify the path of python script and conduct co-simulation with EnergyPlus .

## Here is the python code

```python
"""
 	This python script is the example of CosimR to show how to do co-simulation with EnergyPlus
 	Package: CosimR
	Github:	https://github.com/jywang2016/CosimR
	Author: Jiangyu Wang
	Date: 11th Dec, 2018
	Email: jywang_2016@hust.edu.cn
	Reference: schedule example in BCVTB
"""

import re
import sys

string = sys.argv[1]
time = sys.argv[2]
iter = sys.argv[3]

m = re.findall(r"\d+\.?\d*",string)

tout = float(m[0])

# input const -----------------------
dayStart = 6*3600
nightStart = 16*3600
TCNight = 30
TCRooLow = 22
TCRooHig = 26

TCOutLow = 20
TCOutHig = 24

THDay = 20
THNight = 16

# temp set logic ----------------------
time = int(float(time))

ToutDif = tout - TCOutLow

TSetCooOn = TCRooLow + ToutDif * (TCRooHig - TCRooLow)/(TCOutHig - TCOutLow)
TCDay = max(TCRooLow,min(TCRooHig,TSetCooOn))

if time % 86400 > dayStart and time % 86400 < nightStart:
	THSetPoi = THDay
	TCSetPoi = TCDay
else:
	THSetPoi = THNight
	TCSetPoi = TCNight

strs = [str(THSetPoi),str(TCSetPoi),' ']

sys.stdout.write(','.join(strs))

```
Suppose the python code `Cosim.py` will be placed into the `python` folder under the `xmlpath = 'D:/bcvtb/examples/CosimRtest'`.

## Co-simulation by using CosimR

```{r}
library(CosimR)
```

Step1: generate the .xml file

```{r,eval=TRUE}
xmlpath = 'D:/bcvtb/examples/CosimRtest'
copy_xml(xmlpath = xmlpath)
```

Step2: modify the .xml file

```{r}
file.copy(from = system.file("extdata/Cosim.py", package = "CosimR"),
          to = paste0(xmlpath,'/python'),
          overwrite = TRUE)

xmlroot<- modify_xml(xmlpath = xmlpath,
                     timeStep = 15*60, 
                     beginTime = 3*24*3600,
                     endTime = 4*24*3600,
                     extractLength = 2,
                     idf = paste0(xmlpath,'/SmOffPSZ.idf'),
                     epw = 'D:/bcvtb/examples/ePlusWeather/USA_IL_Chicago-OHare.Intl.AP.725300_TMY3.epw',
                     outname = 'eplusout',
                     programname = 'python',
                     programArgs = 'Cosim.py',
                     workingDir = paste0(xmlpath,'/python'),
                     cpp = FALSE)
```

Step3: save the .xml file

```{r}
write_xml(rootnode = xmlroot,
          xmlpath = xmlpath,
          output = 'new.xml')
```

Step4: run the .xml file

```{r,eval=FALSE}
run_Cosim(bcvtbpath = 'D:/bcvtb',
          xmlpath = xmlpath,
          output = 'new.xml')
```

## Add plotter in BCVTB manually

Plotter block is not included in the .xml template file provided in the `CosimR` package. If you want see the results in real time, add plotter block in BCVTB manually is a good choice.